### 2016-12-10 paper/evaluation.tex
updating rq1

To evaluate the frequency of time-consuming regression tests, we
considered the \Fix{X} Maven projects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} illustrates the commands used in our
scripts to test each subject.  To avoid inflating the measured time,
we first compile the sources files (line 1) and later, we ran the
tests ignoring non-related tasks (line 3).  In addition, when we run a
subject's test suite, we operate Maven in offline mode to limit the
network access, avoiding any unnecessary package update as all
required \emph{jars} are available locally (line 2). We also
considered the execution of all subjects enforcing sequential
execution to avoid having the real time cost masked by the use of any
parallel setting mentioned in Section~\ref{sec:modes} (line 4).  After
the test execution, we use a simple regular expression over the
builder output to extract the elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip, go, offline, P},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn dependency:go-offline
mvn -o test -Dmaven.javadoc.skip=true
mvn -o test -Dmaven.javadoc.skip=true -P tests-seq
\end{lstlisting}
\caption{\label{fig:mvn-execution} Maven commands to test a subject:
    line 1 compiles all subject's source artifacts and make them
    available in a local repository (\ie, directory \emph{.m2} in the
    user's home directory); line 2 ensures all dependencies are
    resolved; line 3 runs the tests in offline mode ignoring javadoc
    generation; line 4 runs the tests using our \emph{tests-seq}
    profile to ensure sequential execution.}
\end{figure}

>>>>

To evaluate the frequency of time-consuming regression tests, we
considered the 321 subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} illustrates the commands used in our
scripts to test each subject.  To avoid inflating the measured time,
we first compile the sources files (line 1) and later, we ran the
tests ignoring non-related tasks (line 3).  In addition, when we run a
subject's test suite, we operate Maven in offline mode to limit the
network access, avoiding any unnecessary package update as all
required \emph{jars} are available locally (line 2).  After the test
execution, we use a simple regular expression over the builder output
to extract the elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip, go, offline, P},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn dependency:go-offline
mvn -o test -Dmaven.javadoc.skip=true
\end{lstlisting}
\caption{\label{fig:mvn-execution} Maven commands to test a subject:
    line 1 compiles all subject's source artifacts and make them
    available in a local repository (\ie, directory \emph{.m2} in the
    user's home directory); line 2 ensures all dependencies are
    resolved; line 3 runs the tests in offline mode ignoring javadoc
    generation.}
\end{figure}
